% This file is the LaTeX source for Nicolas Gamboa Alvarez's CV (English).
% Nicolas Gamboa Alvarez, 2026

\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.5in,top=0.2in,right=0.5in,bottom=0.5in]{geometry} % Document margins
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{fontawesome}
\usepackage{relsize}
\usepackage{graphicx}

\sloppy



\newcommand{\tab}[1]{\hspace{.1\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\name{Nicolas Gamboa Alvarez} % Your name
\title{Msc in Financial Engineering} % Your title


%
%   CONTACT INFORMATION
%

\address{\faPhoneSquare \ +33 (0)6 14 42 18 03} % Phone number
\address{Paris, France} % Address (not full)
\address{\href{mailto:nicolas.gamboaalvarez@edhec.com}{\faEnvelopeSquare \ nicolas.gamboaalvarez@edhec.com} \\ \href{https://www.linkedin.com/in/nicolasgamboaalvarez} {\faLinkedinSquare \ LinkedIn: nicolasgamboaalvarez} \\ \href{https://github.com/nicgambalva}{\faGithubSquare \ GitHub: nicgambalva}} % Mail, LinkedIn and GitHub
%\photo{photo/IMG_6035.jpeg}

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\begin{document}



%
%   EDUCATION SECTION
%

\begin{rSection}{EDUCATION}

\begin{rSubsection}{EDHEC Business School}{August 2022 - July 2025}{Programme Grande École - Msc in Financial Engineering / Master in Management in Finance}{Nice, France}
    \item Recently ranked as the 4th best MiM and 6th best Master in Finance worldwide according to the Financial Times.
    \item \textit{Relevant courses: Financial Econometrics with R, Financial Machine Learning, Volatility Based Portfolio Construction Strategies (Master Project), Quantitative Portfolio Management, Advanced Derivatives, Equity Derivatives}
\end{rSubsection}

\begin{rSubsection}{Universidad de los Andes}{August 2015 - November 2021}{Bachelor in Economics}{Bogota, Colombia}
    \item Recognized as the best Economics program in Colombia and the 4th best in Latin America by QS Rankings.
    \item \textit{Relevant Courses: Asset Management, Capital Markets, AI and Big Data for Economics}
\end{rSubsection}

\end{rSection}



%
%   WORK EXPERIENCE SECTION
%

% filepath: /Users/nicolasgamboaalvarez/Documents/Projects/Curriculum-Vitae/Curriculum Vitae/CV.tex
\begin{rSection}{WORK EXPERIENCE}

    \begin{rSubsection}{CANDRIAM}{August 2024 - January 2026}{Assistant Client Portfolio Manager for Liquid Alternative Funds - Internship}{Paris, France}
        \item Supported liquid alternative funds across equity market neutral, merger arbitrage, CTA and multi-asset premia, as Assistant Client Portfolio Manager. Interfaced daily with Portfolio Managers and addressed client inquiries.
        \item Prepared fund comments, performance reports, and presentations explaining investment strategies. Automated reporting workflows using Python, Bloomberg, VBA, and Azure.
    \end{rSubsection}

    \begin{rSubsection}{TP ICAP}{January 2024 - July 2024}{Quantitative Analyst / Big Data Equity Research - Internship}{Paris, France}
        \item Performed quantitative research on 243 listed equities in 18 stock exchanges and 7 MSCI indexes. Used big data solutions to identify investment opportunities, particularly forecasting earnings surprises.
        \item Developed and implemented quantitative models using large datasets. Tracked and predicted earnings of listed companies and the performance of equity indexes using Python and R.
        \item Wrote research and market insight reports on companies under coverage. Tested our research following earnings releases. 
    \end{rSubsection}

    \begin{rSubsection}{PKF Arsilon}{June 2023 - December 2023}{Financial Modelling and Valuation Consultant - Internship}{Paris, France}
        \item Valued companies, debt instruments, lease agreements, and management packages. Analyzed financial data and business plans and conducted market research to support valuations.
        \item Built Excel, CapitalIQ Pro, and VBA valuation models for equities, bonds, management packages, and other financial instruments. 
        \item Implemented valuation methods such as binomial trees, Monte Carlo simulations, DCFs and comparables analysis.
    \end{rSubsection}

    \begin{rSubsection}{EY - Technology Consulting}{July 2021 - August 2022}{Data \& Analytics Consultant - Internship}{Bogota, Colombia}
        \item Implemented algorithms for data analysis in Python and R for different clients. Simulated yield and risk scenarios using statistical models and visualization techniques. 
        \item Created data-driven reports and dashboards in Power BI. Compiled, prepared, and analyzed multiple data sources and supported database design and mathematical modeling.
        \item Built data models and data architectures for clients in different industries.
    \end{rSubsection}
\end{rSection}



%
%   ADDITIONAL EXPERIENCE AND ACHIEVEMENTS SECTION
%

%\begin{rSection}{ADDITIONAL EXPERIENCE AND ACHIEVEMENTS}

%\begin{rSubsection}{Finance and Investment Club Uniandes (FIC)}{March 2020 – November 2021}{Finance student association of the University of the Andes}{Bogota, Colombia}
%    \item Created and managed an international Fintech podcast "Fintech: Byte-Sized" with 12 episodes and over 1800 listens, by researching, developing topics, and conducting interviews.
% \%end{rSubsection}

%\begin{rSubsection}{Andrés Bello Distinction}{December 2014}{Best results on the country's university admission tests}{Bogota, Colombia}
%    \item Sixth best score in the country, and second best in Bogota.
%\end{rSubsection}

%\end{rSection}

%
%   TECHNICAL STRENGTHS SECTION
%

\begin{rSection}{TECHNICAL STRENGTHS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages &  Python, R, SQL, VBA, \LaTeX\\
Software \& Tools & MS Excel, MS PowerPoint, Power BI \\
Financial databases & Bloomberg, S\&P Capital IQ Pro, FactSet \\
\end{tabular}

\end{rSection}

%
%   LANGUAGES SECTION
%

\begin{rSection}{LANGUAGES}

{\bf French:} \ \ {Fluent - C2} \hfill {\bf English:} \ \ {Fluent - C2} \hfill {\bf Spanish:} \ \ {Native - C2} \hfill {\bf German:} \ \ {Advanced - B2}

\end{rSection}


%
%   HOBBIES AND INTERESTS SECTION
%




\begin{rSection}{HOBBIES AND INTERESTS}

    {\bf Swimming} \ \ \ \ \ {\bf Golf} \ \ \ \ \ {\bf Film} \ \ \ \ \ {\bf Specialty coffee}
    
\end{rSection}



\end{document}
