%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.5in,top=0.2in,right=0.5in,bottom=0.5in]{geometry} % Document margins
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{fontawesome}
\usepackage{relsize}
\usepackage{graphicx}

\sloppy



\newcommand{\tab}[1]{\hspace{.1\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\name{Nicolás Gamboa Álvarez} % Your name

%
%   CONTACT INFORMATION
%

\address{\faPhoneSquare \ +33 (0)6 14 42 18 03} % Phone number
\address{Paris, France} % Address (not full)
\address{\href{mailto:nicolas.gamboaalvarez@edhec.com}{\faEnvelopeSquare \ nicolas.gamboaalvarez@edhec.com} \\ \href{https://www.linkedin.com/in/nicolasgamboaalvarez} {\faLinkedinSquare \ LinkedIn: nicolasgamboaalvarez}} % Mail and LinkedIn
%\photo{photo/IMG_6035.jpeg}

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\begin{document}

%
%   EDUCATION SECTION
%

\begin{rSection}{EDUCATION}

\vspace{0.3em}
\begin{rSubsection}{EDHEC Business School}{August 2022 - Present}{Programme Grande École}{Nice, France}
    Double degree Master in Management (MiM) in Finance / MSc in Financial Engineering.
    \item Recently ranked as the 4th best MiM and 6th best Master in Finance worldwide according to the Financial Times.
    \item \textit{Relevant courses: Private Equity and Debt, Infrastructure, Hedge Funds, Real Estate, Financial Machine Learning, Volatility Based Portfolio Construction Strategies (Master Project), Quantitative Portfolio Management, Advanced Derivatives}
\end{rSubsection}

\begin{rSubsection}{Universidad de los Andes}{August 2015 - November 2021}{Bachelor in Economics,  Bachelor in Business Administration}{Bogota, Colombia}
    \item Recognized as the best Economics program in Colombia and the 4th best in Latin America by QS Rankings.
    \item \textit{Relevant Courses: Asset Management, Capital Markets, AI and Big Data for Economics}
\end{rSubsection}

\end{rSection}

\vspace{0.5em}

%
%   WORK EXPERIENCE SECTION
%

\begin{rSection}{WORK EXPERIENCE}

    \vspace{0.3em}
    \begin{rSubsection}{TP ICAP}{January 2024 - July 2024}{Financial analyst - Big Data + Equity research - Internship}{Paris, France}
        \item Implemented big data analytics for equity research, to uncover investment opportunities and pricing discrepancies over a portfolio of 243 listed equities in 18 stock exchanges. Developed forecasting models for micro and macro trends.
        \item Conducted quantitative research of 7 MSCI indexes, and evaluated financial performance of listed equities and indexes. Established client relationships, monitored market trends, and authored 10+ summaries of research and market insights.
    \end{rSubsection}
    
    \begin{rSubsection}{PKF Arsilon}{June 2023 - December 2023}{Financial modelling and valuation consultant - Internship}{Paris, France}
        \item Built 10+ Excel, CapitalIQ Pro, and VBA valuation models for equities, bonds, management packages, and other contracts. Utilized advanced techniques like trinomial trees and Monte Carlo simulations.
        \item Analyzed financial data and business plans to value 10+ companies and other different types of financial assets. Applied relevant valuation techniques and conducted research on comparables. %providing actionable insights to asset managers and financial directors.
    \end{rSubsection}
    
    \begin{rSubsection}{EY - Technology Consulting}{July 2021 - August 2022}{Data \& analytics consultant - Internship}{Bogota, Colombia}
        \item Implemented algorithms for data analysis in Python and R, including simulation of yield and risk scenarios using statistical models for 4 types of assets. Contributed to the development of data science tools.
        \item Created 10+ data-driven reports and dashboards as client deliverables, which implied compilation, preparation, and analysis of different data sources into Power BI. Supported the design of databases and mathematical modelling.
    \end{rSubsection}
    \end{rSection}
    
    \vspace{0.5em}

%
%   ADDITIONAL EXPERIENCE AND ACHIEVEMENTS SECTION
%

\begin{rSection}{ADDITIONAL EXPERIENCE AND ACHIEVEMENTS}

\vspace{0.3em}
\begin{rSubsection}{Finance and Investment Club Uniandes (FIC)}{March 2020 – November 2021}{Finance student association of the University of the Andes}{Bogota, Colombia}
    \item Created and managed an international Fintech podcast "Fintech: Byte-Sized" with 12 episodes and over 1800 listens, by researching, developing topics, and conducting interviews.
\end{rSubsection}

\begin{rSubsection}{Andrés Bello Distinction}{December 2014}{Best results on the country's university admission tests}{Bogota, Colombia}
    \item Sixth best score in the country, and second best in Bogota.
\end{rSubsection}

\end{rSection}

\vspace{0.5em}

%
%   TECHNICAL STRENGTHS SECTION
%

\begin{rSection}{TECHNICAL STRENGTHS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages &  Python, R, VBA, Matlab, \LaTeX, currently learning C++ \\
Software \& Tools & MS Excel, MS PowerPoint, Power BI \\
Financial databases & Bloomberg, Refinitiv, S\&P Capital IQ Pro, FactSet \\
\end{tabular}

\end{rSection}

\vspace{0.5em}

%
%   LANGUAGES SECTION
%

\begin{rSection}{LANGUAGES}

{\bf Spanish} \ \ {Native - C2} \hfill {\bf English} \ \ {Fluent - C2} \hfill {\bf French} \ \ {Fluent - C2} \hfill {\bf German} \ \ {Advanced - B2}

\end{rSection}

\vspace{0.5em}

%
%   HOBBIES AND INTERESTS SECTION
%




\begin{rSection}{HOBBIES AND INTERESTS}

{\bf Swimming (pool and open water)} \ \ \ \ \ {\bf Film and cinematography} \ \ \ \ \ {\bf Golf} 

\end{rSection}


\end{document}
