%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.5in,top=0.2in,right=0.5in,bottom=0.5in]{geometry} % Document margins
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{fontawesome}
\usepackage{relsize}
\usepackage{graphicx}

\sloppy



\newcommand{\tab}[1]{\hspace{.1\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\name{Nicolás Gamboa Álvarez} % Your name

%
%   CONTACT INFORMATION
%

\address{\faPhoneSquare \ +33 (0)6 14 42 18 03} % Phone number
\address{Paris, France} % Address (not full)
\address{\href{mailto:nicolas.gamboaalvarez@edhec.com}{\faEnvelopeSquare \ nicolas.gamboaalvarez@edhec.com} \\ \href{https://www.linkedin.com/in/nicolasgamboaalvarez} {\faLinkedinSquare \ LinkedIn: nicolasgamboaalvarez} \\ \href{https://github.com/nicgambalva}{\faGithubSquare \ GitHub: nicgambalva}} % Mail, LinkedIn and GitHub
%\photo{photo/IMG_6035.jpeg}

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\begin{document}



%
%   WORK EXPERIENCE SECTION
%

% filepath: /Users/nicolasgamboaalvarez/Documents/Projects/Curriculum-Vitae/Curriculum Vitae/CV.tex
\begin{rSection}{WORK EXPERIENCE}

    \begin{rSubsection}{CANDRIAM}{August 2025 - Present}{Assistant Client Portfolio Manager Liquid Alternatives - Internship}{Paris, France}
        \item Product specialist for liquid alternative strategies, including Absolute Return Equity Market Neutral, Merger Arbitrage, and Multi-Asset Premia. Responsible for monitoring and reviewing the performance of these strategies, and for preparing investment presentations for prospect clients.
        \item Prepare and update fund comments, fund reviews, performance reports, and investment strategy presentations. Interface daily with Portfolio Managers and respond to client inquiries.
    \end{rSubsection}

    \begin{rSubsection}{TP ICAP}{January 2024 - July 2024}{Quantitative Analyst / Big Data Equity Research - Internship}{Paris, France}
        \item Worked as a quantitative analyst in a big data equity research team, focusing on predicting earnings call surprises using large and diverse data sources across hundreds of listed companies.
        \item Developed and implemented quantitative models using large datasets to track and predict earnings of listed companies and the performance of equity indexes, using Python and R.
    \end{rSubsection}

    \begin{rSubsection}{PKF Arsilon}{June 2023 - December 2023}{Financial Modelling and Valuation Consultant - Internship}{Paris, France}
        \item Built 10+ Excel, CapitalIQ Pro, and VBA valuation models for equities, bonds, management packages, and other contracts. Implemented advanced techniques like trinomial trees and Monte Carlo simulations.
        \item Analyzed financial data and business plans to value 10+ companies and other different types of financial assets. Applied relevant valuation techniques and conducted market research.
    \end{rSubsection}

    \begin{rSubsection}{EY - Technology Consulting}{July 2021 - August 2022}{Data \& Analytics Consultant - Internship}{Bogota, Colombia}
        \item Implemented algorithms for data analysis in Python and R for different clients, including simulation of yield and risk scenarios using statistical models and visualization techniques. Contributed to the development and implementation of data science tools.
        \item Created 10+ data-driven reports and dashboards as client deliverables, which implied compilation, preparation, and analysis of different data sources into Power BI. Supported the design of databases and mathematical modelling.
    \end{rSubsection}
\end{rSection}


%
%   EDUCATION SECTION
%

\begin{rSection}{EDUCATION}

\begin{rSubsection}{EDHEC Business School}{August 2022 - July 2025}{Programme Grande École - Msc in Financial Engineering / Master in Management (MiM) in Finance}{Nice, France}
    \item Recently ranked as the 4th best MiM and 6th best Master in Finance worldwide according to the Financial Times.
    \item \textit{Relevant courses: Financial Econometrics with R, Financial Machine Learning, Volatility Based Portfolio Construction Strategies (Master Project), Quantitative Portfolio Management, Advanced Derivatives, Equity Derivatives}
\end{rSubsection}

\begin{rSubsection}{Universidad de los Andes}{August 2015 - November 2021}{Bachelor in Economics,  Bachelor in Business Administration}{Bogota, Colombia}
    \item Recognized as the best Economics program in Colombia and the 4th best in Latin America by QS Rankings.
    \item \textit{Relevant Courses: Asset Management, Capital Markets, AI and Big Data for Economics}
\end{rSubsection}

\end{rSection}



%
%   ADDITIONAL EXPERIENCE AND ACHIEVEMENTS SECTION
%

%\begin{rSection}{ADDITIONAL EXPERIENCE AND ACHIEVEMENTS}

%\begin{rSubsection}{Finance and Investment Club Uniandes (FIC)}{March 2020 – November 2021}{Finance student association of the University of the Andes}{Bogota, Colombia}
%    \item Created and managed an international Fintech podcast "Fintech: Byte-Sized" with 12 episodes and over 1800 listens, by researching, developing topics, and conducting interviews.
% \%end{rSubsection}

%\begin{rSubsection}{Andrés Bello Distinction}{December 2014}{Best results on the country's university admission tests}{Bogota, Colombia}
%    \item Sixth best score in the country, and second best in Bogota.
%\end{rSubsection}

%\end{rSection}

%
%   TECHNICAL STRENGTHS SECTION
%

\begin{rSection}{TECHNICAL STRENGTHS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages &  Python, R, VBA, \LaTeX\\
Software \& Tools & MS Excel, MS PowerPoint, Power BI \\
Financial databases & Bloomberg, Refinitiv, S\&P Capital IQ Pro, FactSet \\
\end{tabular}

\end{rSection}

%
%   LANGUAGES SECTION
%

\begin{rSection}{LANGUAGES}

{\bf Spanish} \ \ {Native - C2} \hfill {\bf English} \ \ {Fluent - C2} \hfill {\bf French} \ \ {Fluent - C2} \hfill {\bf German} \ \ {Advanced - B2}

\end{rSection}


%
%   HOBBIES AND INTERESTS SECTION
%




\begin{rSection}{HOBBIES AND INTERESTS}

    {\bf Swimming} \ \ \ \ \ {\bf Golf} \ \ \ \ \ {\bf Film} \ \ \ \ \ {\bf Specialty coffee}
    
\end{rSection}



\end{document}
